### 2024-01-10 documentation/thesis/thesis_document.tex
more thesis

\ref{usecases}

@@

The next initialisation system is dedicated for multi-sensor
synchronisation \ref{sensor-syncronsisation-interface}. The last step in
the setup is to configure communication with the host or connected
\gls{pc}. All implemented microcontroller platforms used (Raspberry Pi
Pico, STM32F4) have a \gls{usb} slave port. The used usb descriptor is a
\gls{usb} \gls{cdc}. This is used to emulate a virtual RS232
communication port using a \gls{usb} port on a \gls{pc} and usually no
additional driver is needed on modern host systems.

@@

Ring buffers are well suited for applications with variable data rates
and minimise the need for complex memory management. The buffer can be
read out by command and the result of the measurement is sent to the
host. Each sensor measurement result is transmitted from the buffer to
the host together with a time stamp and a sequential number. This
ensures that in a multi-sensor setup with several sensors. The
measurements are synchronized \ref{sensor-syncronsisation-interface} in
time and are not out of sequence or drift.

@@

\hypertarget{sensor-syncronsisation-interface}{%
\subsection{Sensor syncronsisation
interface}\label{sensor-syncronsisation-interface}}

@@

To enhance the accessibility and interpretability of the recorded data,
a dedicated module, MRPMagnetTypes, comes into play. This module is
specifically designed for the storage of physical parameters pertaining
to the magnets targeted for measurement. By centralizing this
information, users can streamline the subsequent phases of evaluation
and analysis, simplifying the overall process and ensuring a more
efficient and insightful exploration of the collected data.

At the end of processing, the collected data is typically exported;
various functions are provided for this purpose. These are described as
the following.

@@

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!MRPReadingSourceStatic!} - for 1D and 2D
  sensor such as
  \passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor}
\item
  \passthrough{\lstinline!MRPReadingSourceFullsphere!} - for 3D sensors
  such as \passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere}
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!MRPVisualization!} - different table, graph
  based plots
\item
  \passthrough{\lstinline!MRPPolarVisualization!} - fullsphere map plots
\end{itemize}

@@

@@

At the current described scenarios, it is only possible to detect and
use sensors that are directly connected to the host \gls{pc}. It has the
disadvantage that there must always be a physical connection. This can
make it difficult to install multiple sensors in measurement setups
where space or cable routing options are limited. So multibe sensor can
be connected to a \passthrough{\lstinline!remote!} \gls{pc} which is
available on the network. This can be a \gls{sbc} (e.g.~a Raspberry Pi).
The small footprint and low power consumption make it a good choice. It
can also be used in a temperature chamber.

@@

Another important aspect when using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the \gls{usb} interface. If
several sensors are connected locally, they can be connected to each
other via their sync input using short cables. One sensor acts as the
central clock as described in \ref{sensor-syncronsisationiinterface}.
this no longer works for long distances and the syncronisation must be
made via a shared network connection.

>>>>

The present work aims to provide an efficient and comprehensive solution
for the design of low-field MRI devices by developing and implementing a
software and hardware framework.

The scope of the software library is to lay the foundation for the
systematic characterization of magnets based on permanent magnets. The
library will enable data acquisition, storage and analysis of magnetic
properties, with customization possible at each step of the process. The
work aims to facilitate magnetic field characterization and improve the
exchange of data between different user groups. Complete documentation,
tutorials and tests will enable users to use the framework efficiently
and adapt it to their specific requirements. The application of the
developed framework for the characterization of different magnets and
the integration of magnetic field sensors serve as practical
applications and validation of the developed solution.

@@

The next initialisation system is dedicated for multi-sensor
synchronisation \ref{sensor-syncronisation-interface}. The last step in
the setup is to configure communication with the host or connected
\gls{pc}. All implemented microcontroller platforms used (Raspberry Pi
Pico, STM32F4) have a \gls{usb} slave port. The used usb descriptor is a
\gls{usb} \gls{cdc}. This is used to emulate a virtual RS232
communication port using a \gls{usb} port on a \gls{pc} and usually no
additional driver is needed on modern host systems.

@@

Ring buffers are well suited for applications with variable data rates
and minimise the need for complex memory management. The buffer can be
read out by command and the result of the measurement is sent to the
host. Each sensor measurement result is transmitted from the buffer to
the host together with a time stamp and a sequential number. This
ensures that in a multi-sensor setup with several sensors. The
measurements are synchronized \ref{sensor-syncronisation-interface} in
time and are not out of sequence or drift.

@@

\hypertarget{sensor-syncronisation-interface}{%
\subsection{Sensor Syncronisation
Interface}\label{sensor-syncronisation-interface}}

@@

To enhance the accessibility and interpretability of the recorded data,
a dedicated module, \passthrough{\lstinline!MRPMagnetTypes!}, comes into
play. This module is specifically designed for the storage of physical
parameters pertaining to the magnets targeted for measurement. By
centralizing this information, users can streamline the subsequent
phases of evaluation and analysis, simplifying the overall process and
ensuring a more efficient and insightful exploration of the collected
data.

At the end of processing, the collected and modified data are typically
exported; various functions are provided for this purpose. This process
is described in the following subchapter.

@@

The extention modules build on the core modules and offer the user
additional basic functionalities. These include functions for data
acquisition, visualization and analysis.

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!MRPReadingSourceStatic!} - for 1D and 2D
  sensors such as
  \passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor}
\item
  \passthrough{\lstinline!MRPReadingSourceFullsphere!} - for 3D sensors
  such as \passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere}
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!MRPVisualization!} - different table and graph
  based plots
\item
  \passthrough{\lstinline!MRPPolarVisualization!} - fullsphere map plots
\end{itemize}

@@

Data analysis offers the user the greatest flexibility to implement
their own modules. For this reason \passthrough{\lstinline!MRPAnalysis!}
contains functions for calculating the following data analyses, which
are compatible with class instances of
\passthrough{\lstinline!MRPReading!}:

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!std\_deviation!} - standard deviation
\item
  \passthrough{\lstinline!mean!} - mean value
\item
  \passthrough{\lstinline!variance!} - variance
\item
  \passthrough{\lstinline!center\_of\_gravity!} - center of gravity
\item
  \passthrough{\lstinline!binning!} - distribution of a sample by means
  of a histogram
\item
  \passthrough{\lstinline!k-nearest!} - k-nearest neighbors
\end{itemize}

In addition, the export function
\passthrough{\lstinline!.to\_numpy\_matrix!} enables further processing
of the data in the
\passthrough{\lstinline!Numpy!}\cite{harris2020array} framework, in
which many other standard analysis functions are implemented.

@@

At the current described scenarios, it is only possible to detect and
use sensors that are directly connected to the host \gls{pc}. It has the
disadvantage that there must always be a physical connection. This can
make it difficult to install multiple sensors in measurement setups
where space or cable routing options are limited. So multibe sensor can
be connected to any \gls{pc} which is available on the network. This can
be a \gls{sbc} (e.g.~a Raspberry Pi). The small footprint and low power
consumption make it a good choice. It can also be used in a temperature
chamber.

@@

Another important aspect when using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the \gls{usb} interface. If
several sensors are connected locally, they can be connected to each
other via their sync input using short cables. One sensor acts as the
central clock as described in \ref{sensor-syncronisation-interface}.
this no longer works for long distances and the syncronisation must be
made via a shared network connection.
